Algorithm explanation

### 2013-08-20 article/algo.tex
Examples introduced for algorithm explanation
Updated examples

>>>>

First, consider the following example.

\begin{align*}
x \leq 1 & \implies A(x) \\
y \leq 2 & \implies B(y) \\
A(x) \wedge B(y) & \implies 3x+2y \leq 10
\end{align*}

In this example, a simple solution is expressed by linear expression
templates, whose coefficients and constants are parameterized. Assume
that they have following predicate templates.

\begin{align*}
A(x) : c_1 x + c_2 \leq 0 \\
B(y) : c_3 y + c_4 \leq 0
\end{align*}

By naturally encoding every Horn clause with Farkas's lemma
constraints, we obtain the following linear constraint over
$c_i$.

\begin{align*}
\lambda_1 = c_1 \wedge - \lambda_1 \geq c_2 \wedge \\
\lambda_2 = c_3 \wedge - 2 \lambda_2 \geq c_4 \wedge \\
c_1 = 3 \lambda_3 \wedge c_3 = 2 \lambda_3 \wedge c_2 + c_4 \geq -10 \lambda_3 \wedge \\
\lambda_1 \geq 0 \wedge \lambda_2 \geq 0 \wedge \lambda_3 \geq 0
\end{align*}

One of the model satisfying the constraint above is

\begin{align*}
\left\lbrace c_1 = 3 \wedge c_2 = -3 \wedge c_3 = 2 \wedge c_4 = -4 \wedge
\lambda_1 = 3 \wedge \lambda_2 = 2 \wedge \lambda_3 = 1 \right\rbrace
\end{align*}

Second, we explain a case that some predicate variables appear
multiple times on left-hand side in different Horn clauses.

\begin{align*}
x \leq 1 & \implies A(x) \\
A(x) \wedge A(y) & \implies x+y \leq 2
\end{align*}

Finally, we explain a case that an input set of Horn clauses contain
disjunctions on left-hand side.

\begin{align*}
x \leq 0 \wedge -x \leq 0 & \implies A(x) \\
x+1 \leq 0 \vee -x+1 \leq 0 & \implies B(x) \\
A(x) \wedge B(x) & \implies 1 \leq 0
\end{align*}
